Robust Adaptation to Multi-Scale Climate Variability

### 2019-01-09 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
Incorporate manu comments

Typical climate risk management policies do not use a single risk mitigation instrument, but rather build a portfolio of several instruments.
Each has its own planning period, which may be separate from the planning horizon of the portfolio as a whole.
This means that even if the portfolio has a long planning period, \ie if long-term plans are a priority, this long-term plan may be achieved through a series of flexible and adaptive instruments with short individual planning periods.
The costs and benefits of each individual instrument will be assessed over its individual, finite planning period, but decisions about the portfolio structure are evaluated over the longer planning horizon.

@@

The first step is to sample climate risk by generating synthetic streamflow sequences.
To do this, we model  annual-maximum flood peaks following a log-normal distribution, conditional on a location parameter which may vary in time:
\begin{equation} \label{eq:log-normal}
  \log Q(t) \sim \normal \qty(\mu(t), \sigma(t)).
\end{equation}
We further assume a constant coefficient of variation of the log streamflow,
\begin{equation}
  \sigma(t) = \xi \mu(t)  
\end{equation}
and apply a lower threshold on the standard deviation
\begin{equation}
  \sigma(t) \geq \sigma_\text{min} > 0.
\end{equation}
This flexible framing describes the \begin{enumerate*}[label= (\roman*)]
  \item \gls{lfv} only;
  \item \gls{lfv} plus secular change; and
  \item secular change only
\end{enumerate*}
scenarios in a single equation; the only component which needs to change is the dependence of $\mu(t)$ on time, which we parameterize as
\begin{equation}\label{eq:nino3}
  \mu(t) = \mu_0 + \beta x(t) + \gamma \qty(t - t_0),
\end{equation}
where $x(t)$ represents a climate time series which itself exhibits \gls{lfv}.
This parameterization is analagous to the ``climate-informed'' approach described in several studies for estimating climate risk \citep{Delgado:2014ey,Merz:2014gf,Farnham:2018gs}.
Thus, when $\beta \neq 0$ there will be \gls{lfv}, and when $\gamma \neq 0$ there will be secular change.
The values of all parameters used for sampling climate risk are listed in \cref{sec:supp-methods} for each of the three scenarios considered.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{M-N-Sketch.pdf}
  \caption{
    The importance of predicting different signals, and the identifiability and predictability of the signals, depends on the degree of informational uncertainty ($N$) and the project planning period ($M$).
  }\label{fig:m-n-sketch}
\end{figure}
We also showed that the importance of predicting different climate signals, and potential for doing so skillfully, depend on the project planning period $M$ and the information available, $N$.
\Cref{fig:m-n-sketch} shows that when $M$ and $N$ are short, only a ``rough guess'' using simple models is feasible, and more complex models  only add uncertainty.
As $N$ increases, however, the potential for skillful prediction of \gls{lfv} over the short planning period increases, thereby reducing the cost of a flexible or adaptive instrument.
If $M$ is large, \ie a permanent plan is considered, then informational uncertainty may be addressed with sufficient information (large $N$), but large intrinsic uncertainty may remain.
Finally, if $M$ is long but $N$ is short, then the analysis will lead to the ``danger zone'' of extrapolation and a high potential for misleading estimates.

>>>>

Typical climate risk management policies do not use a single risk mitigation instrument, but rather build a portfolio of several instruments.
Each has its own operational period, which may or may not match the planning horizon of the portfolio as a whole.
This means that even if the portfolio has a long planning period, \ie if long-term plans are a priority, this long-term plan may be achieved through a series of flexible and adaptive instruments with short individual planning periods.
The costs and benefits of each individual instrument will be assessed over its individual, finite planning period, but decisions about the portfolio structure are evaluated over the longer planning horizon.

A critical point for decision-making under uncertainty is that if precise climate information over the next few years is available, then this can significantly alter the choice between a large, long-duration project which may take over a year to construct, and a sequence of smaller, short duration projects that can be executed quickly.
For example, if there is credible information that the risk to be mitigated will be much higher in the next few years, then a more costly project would be justified under traditional \gls{cba}.
However, if the construction period were too long, a financial risk mitigation instrument might be needed in the immediate term to cover potential losses before the large project is constructed.
Conversely, if the near term risk is projected to be low, then deferral of the large, expensive project may be warranted, and smaller or nonstructural alternatives may be preferred.
If the risk changes in a cyclical manner, then these decisions become even more nuanced, but there may be an opportunity for significantly improving adaptation using a portfolio risk management approach.
Thus, the precision with how near term and long term directions of climate risk evolve plays directly into adaptation choice.

@@

For the sake of presentation we motivate our results through a simple flood risk example.
The points we seek to make apply to other hydroclimatic risks, and in particular those which may be easily characterized through a time series of annual maxima or minima of the process.
The first step is to sample climate risk by generating synthetic streamflow sequences.
To do this, we model  annual-maximum flood peaks following a log-normal distribution, conditional on a location parameter which may vary in time:
\begin{equation} \label{eq:log-normal}
  \log Q(t) \sim \normal \qty(\mu(t), \sigma(t)).
\end{equation}
We further assume a constant coefficient of variation of the log streamflow,
\begin{equation}
  \sigma(t) = \xi \mu(t)  
\end{equation}
and apply a lower threshold on the standard deviation
\begin{equation}
  \sigma(t) \geq \sigma_\text{min} > 0.
\end{equation}
This flexible framing describes the \begin{enumerate*}[label= (\roman*)]
  \item \gls{lfv} only;
  \item \gls{lfv} plus secular change; and
  \item secular change only
\end{enumerate*}
scenarios in a single equation; the only component which needs to change is the dependence of $\mu(t)$ on time, which we parameterize as
\begin{equation}\label{eq:nino3}
  \mu(t) = \mu_0 + \beta x(t) + \gamma \qty(t - t_0),
\end{equation}
where $x(t)$ represents a climate time series which itself exhibits \gls{lfv}.
This parameterization is analagous to the ``climate-informed'' approach described in several studies for estimating climate risk \citep{Delgado:2014ey,Merz:2014gf,Farnham:2018gs}.
Thus, when $\beta \neq 0$ there will be \gls{lfv}, and when $\gamma \neq 0$ there will be secular change.
The values of all parameters used for sampling climate risk are listed in \cref{sec:supp-methods} for each of the three scenarios considered.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{M-N-Sketch.pdf}
  \caption{
    The importance of predicting different signals, and the identifiability and predictability of the signals, depends on the degree of informational uncertainty ($N$) and the project planning period ($M$).
  }\label{fig:m-n-sketch}
\end{figure}
We also showed that the importance of predicting different climate signals, and potential for doing so skillfully, depend on the project planning period $M$ and the information available, $N$.
\Cref{fig:m-n-sketch} shows that when $M$ and $N$ are short, only a ``rough guess'' using simple models is feasible, and more complex models  only add uncertainty.
As $N$ increases, however, the potential for skillful prediction of \gls{lfv} over the short planning period increases, potentially favoring implementation of a flexible or adaptive instrument.
If $M$ is large, \ie a permanent plan is considered, then informational uncertainty may be addressed with sufficient information (large $N$), but large intrinsic uncertainty may remain.
Finally, if $M$ is long but $N$ is short, then the analysis will lead to the ``danger zone'' of extrapolation and a high potential for misleading estimates.
